---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r echo=TRUE}
activity <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?

```{r echo=TRUE}
totalstep <- aggregate(steps ~ date, activity, sum)
hist(totalstep$steps,xlab = "Total Steps per Day",main = "Histogram of Total Steps")
mean(totalstep$steps) 
median(totalstep$steps)
```

## What is the average daily activity pattern?

```{r echo=TRUE}
steps_per_interval <- aggregate(steps~interval,activity,mean)
plot(steps_per_interval,type='l')
steps_per_interval$interval[which.max(steps_per_interval$steps)]
```

## Imputing missing values

```{r echo=TRUE}
library(Hmisc)
sum(is.na(activity))
activity_impute <- activity
activity_impute$steps <- impute(activity$steps, fun = mean) 
totalstep_impute <- aggregate(steps ~ date, activity_impute, sum)
hist(totalstep_impute$steps,xlab = "Total Steps per Day (impute missing value)",main = "Histogram of Total Steps")
mean(totalstep_impute$steps) 
median(totalstep_impute$steps)
```
The plot looks slightly different than before imputing missing numbers. The mean value is the same as before, but the median value now matches the mean value. 

## Are there differences in activity patterns between weekdays and weekends?

```{r echo=TRUE}
activity$week <- weekdays(as.Date(activity$date))
weekdays1 <- c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday')
activity$wDay <- factor(activity$week %in% weekdays1, levels = c(FALSE,TRUE), labels = c('weekend','weekday'))
dayavg_activity <- aggregate(steps ~ interval + wDay, data=activity,mean)
ggplot (dayavg_activity, aes(interval,steps)) + geom_line() + facet_grid(wDay ~.)
```

